Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-12-18 Articles/Article 1/main.tex
more commetns

\alert{There needs to be an explanation why log, where is this from. Maybe a reference.}

@@

\alert{Is this equation correct, maybe add a singularity damping factor.}

@@

\add{- choice of velocity profile (gaussian, linear ... maybe could move this part to implementation / experiments)}

@@

\add{
	- include execution times \\
	- PLOT: kernel on robot graphics \\
	- IMPORTANT: maybe add 2D mobile platform results \\
}

>>>>

\alert{There needs to be an explanation why log, where is this from. Maybe a reference. cite: DMP Quaternions article Petrič, Žlajpah, Ude}

@@

\alert{Is this equation correct, ADD a singularity damping factor. Maybe even some variation of a changing damping.}

@@

\add{- choice of velocity profile (gaussian, linear ... maybe could move this part to implementation / experiments) \\}
\add{- maybe first debluring - line convolution operation (if thick walls) - however this might move wall back, which could cause crash }

@@

\add{
	- include execution times \\
	- PLOT: kernel on robot graphics \\
	- IMPORTANT: maybe add 2D mobile platform results \\
	- use pybullet or some engine that tells you distance from obstacles and run the same task, compare distances after execution, smoothness of paths (MAYBE FOR PUBLICATION, NOT CONFERENCE)
}
